SETI in the Spatial-Temporal Survey Domain

### 2019-04-18 paper/ms.tex
add caption

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/optical_haystack}
\caption{
comparison of the 8D ``Cosmic Haystack'' volume fraction defined by \citet{wright2018c} using five optical surveys with varying designs. 
}
\label{fig:hay}
\end{figure}

>>>>

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/optical_haystack}
\caption{
Comparison of the 8-D ``Cosmic Haystack'' SETI search volume fraction, defined by \citet{wright2018c}, computed using five optical surveys with varying designs. The Haystack fraction covered by these optical surveys is 1-2 dex larger than typical SETI programs conducted in the radio.
Evryscope \citet{law2015} is the best survey considered here for SETI work, narrowly beating LSST due to its wide field of view and very dense light curves.}
\label{fig:hay}
\end{figure}
